Fluent statistical computing interfaces for biological data analysis

### 2020-07-16 Rmd/04-intron.Rmd
fix citations

The per base coverage score is estimated directly from one or more BAM files
that represent the units within the experimental design,
along with an optional experimental design table that is returns 
a long-form tidy **GRanges** data structure. The coverage estimation is
computed via the **Rsamtools** package, and
users have the ability to estimate coverage in parallel and drop regions
in the genome where there is no coverage [@rsamtools; @GenomicRanges]. This
representation is tidy, since each row of the resulting **GRanges** data
structure corresponds to position(s) within a given sample with a given 
coverage score alongside any variables such as biological group. While the long-form representation repeats the same information
for a sample within the design, the size of the resulting **GRanges** in
memory can be compressed using run-length encoding for any categorical 
variable. This representation allows us to easily transform the coverage scores
and integrate annotations using the **plyranges** grammar, and visualise traces using **ggplot2** [@Wickham2016-gz].

>>>>

The per base coverage score is estimated directly from one or more BAM files
that represent the units within the experimental design,
along with an optional experimental design table that is returns 
a long-form tidy **GRanges** data structure. The coverage estimation is
computed via the **Rsamtools** package, and
users have the ability to estimate coverage in parallel and drop regions
in the genome where there is no coverage [@rsamtools; @granges]. This
representation is tidy, since each row of the resulting **GRanges** data
structure corresponds to position(s) within a given sample with a given 
coverage score alongside any variables such as biological group. While the long-form representation repeats the same information
for a sample within the design, the size of the resulting **GRanges** in
memory can be compressed using run-length encoding for any categorical 
variable. This representation allows us to easily transform the coverage scores
and integrate annotations using the **plyranges** grammar, and visualise traces using **ggplot2** [@Wickham2016-gz].
